---
title: "Spring Kølsch"
output:
  html_document:
    highlight: tango
    toc: TRUE
    toc_float: true
---

## Why make this?

An attempt at a Kølsch style but with some twists
and a bit more hoppiness. Based on a recipe from Voakes.

Aiming to be a light refreshing summer drink.


## Brewing approach

After tasting a 
few Kølsch they range in taste with some of the german ones being very dry
and a bit bland for my taste. This recipe looks good to add a bit
more flavour and aroma through hops, this still has to be balanced
though. Trying other Kølsch styles (not brewed in Cologne) some have more of
a hoppy flavourful aroma and are not as dry.

Using a two stage mash both lasting for 45 minutes with the intention
to get the crisp dry characteristics from the 63 degree mash and then
bring it up to 67 to give it a bit more body.

The hops are mainly left until late to give a bit more aroma with a focus
on citrus flavours over the traditional spicy and earty tones. Not traditional
but more to my taste!


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Currently used
library(dygraphs)
library(xts)
library(weathermetrics)
library(TTR)
```

```{r get_data, echo=FALSE}
googlesheet <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSpzeMxrRBuTp18pYVro9t13JVyxNPAWZwdYaK8n4s5A-AfMBXMAG6GH37j-ri2LTEeaEDvpUhWPNuT/pub?gid=0&single=true&output=csv"

df <- read.csv(url(googlesheet))
```

```{r dataProcessing, echo=FALSE, message=FALSE, warning=FALSE}
# Convert to a usable date time format
df$DateTime <- as.POSIXct(df$Timestamp, 
                          format = "%m/%d/%Y %H:%M:%S",
                          tz = "PDT")

# data is recorded in farenheit, using weathermetrics library
df$TempC <- fahrenheit.to.celsius(df$Temp, round = 2)

df$TempC_sma <- SMA(df$TempC, n = 10)

# Turn it into an xts object combinging a variable and date time
#
# This will be used for time series analysis plots
temp_xts <- xts(df$TempC, order.by = df$DateTime)
temp_sma_xts <- xts(df$TempC_sma, order.by = df$DateTime)
sg_xts <- xts(df$SG, order.by = df$DateTime)
```

```{r plot_functions, echo=FALSE}
graphstyle <- function(fig){
  
  fig %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) %>%
  # Axis options
  dyAxis("y", 
         label = "Temp (C)", 
         valueRange = c(0, 30)) %>%
    dyOptions(axisLineWidth = 1.5,
          drawGrid = FALSE,
          axisLineColor = "#D3D3D3") %>%
  # Legend options
  dyLegend(show = "follow", 
           hideOnMouseOut = FALSE,
           width = 400)
}

graphstyle2 <- function(fig){
  
  fig %>%
  dyOptions(colors = RColorBrewer::brewer.pal(3, "Set2")) %>%
  # Axis options
  dyAxis("y", 
         label = "Specific Gravity", 
         valueRange = c(1.000, 1.070)) %>%
    dyOptions(axisLineWidth = 1.5,
          drawGrid = FALSE,
          axisLineColor = "#D3D3D3") %>%
  # Legend options
  dyLegend(show = "follow",, 
           hideOnMouseOut = FALSE,
           width = 400)
}

annotationstyle <- function(fig){
  
  fig %>%  
    # Set the responsive behaviour
    dyHighlight(highlightCircleSize = 3, 
                highlightSeriesBackgroundAlpha = 0.2) %>%
    # Add shading to highlight different stages in the process
    dyShading(from = "2018-03-25", to = "2018-03-29", color = "#FFFF99") %>%
    dyShading(from = "2018-03-29", to = "2018-05-15", color = "#ADD8E6") %>%
    dyShading(from = "2018-05-15", to = "2018-06-15", color = "#8FBC8F") %>%
    # Add events to highlight when something occured
    dyEvent("2018-03-29", "Reducing Temperature", labelLoc = "bottom") %>%
    dyEvent("2018-05-15", "Conditioning", labelLoc = "bottom") %>%
    dyEvent("2018-06-15", "Drinking Time", labelLoc = "bottom") %>%
    dyEvent("2018-03-25", "Brew Day", labelLoc = "top") %>%
    dyEvent("2018-03-25", "Primary Fermentation", labelLoc = "bottom")
}
```


## Fermentation and conditioning

A quick fermentation followed by a long lagering period.

A one liter yeast starter was created, aeration to wort was added just by
letting the wort drop from high into the fermenter bucket. The fermentation
was active after a few hours and bubbling happily the morning after brew day.

The main fermenetation was finished within around four days.

Tilt hydrometer sensor had not arrived so no data collected until
it had already gotten close to final gravity.

```{r main_plot, echo=FALSE, fig.width=8, fig.height=3}
dataset <- cbind(temp_xts)
dataset2 <- cbind(sg_xts)
dateWindow <- c("2018-03-23", "2018-06-20")

schedule_t <- dygraph(dataset,
        main = "Temperature Schedule",
        group = "beer") %>%
  dyAxis("x",
         valueRange = dateWindow,
         label = "Time") %>%
  dyRangeSelector(dateWindow = dateWindow)  %>%
  dyOptions(stepPlot = TRUE) 



schedule_sg <- dygraph(dataset2,
        main = "SG Schedule",
        group = "beer") %>%
  dyAxis("x",
         valueRange = dateWindow,
         label = "Time") %>%
  dyRangeSelector(dateWindow = dateWindow)  %>%
  dyOptions(stepPlot = TRUE) 

#schedule_t <- graphstyle(schedule_t)
schedule_t <- graphstyle(schedule_t)
schedule_t <- annotationstyle(schedule_t)
schedule_t

#schedule_sg <- graphstyle2(schedule_sg)
schedule_sg <- graphstyle2(schedule_sg)
schedule_sg <- annotationstyle(schedule_sg)
schedule_sg

```

Looking closer at the temperature profile shows an attempt to lager this batch.
The temperature was reduced by moving the fermenter into a cold cellar.

```{r fermentation_profile, echo=FALSE, fig.width=9, fig.height=3}
dateWindow <- c("2018-03-28", "2018-04-05")

fermentation_temp <- dygraph(dataset,
        main = "Temperature Profile Anotated") %>% 
  dyRangeSelector(dateWindow = dateWindow)  %>%
  dyOptions(stepPlot = TRUE) %>%
  dyRangeSelector(height = 20) %>%
  # Lines to highlight values
  dyLimit(10, color = "blue") 

fermentation_temp <- graphstyle(fermentation_temp)
fermentation_temp
```

